Statistical analysis script

### 2023-04-08 code/analysis_code/statistical_analysis.qmd
update again

# Modifying Test Data Variables to Maintain Compatibility
```{r}
test_data_final
```

@@

>>>>

@@

# Save RDS Files

```{r}
# Illness
save_location <- here("results", "illness_rmse_models.rds")
saveRDS(illness_model_dataframe, file = save_location)

# Hospitalizations
save_location <- here("results", "hospital_rmse_models.rds")
saveRDS(hosp_model_dataframe, file = save_location)
```
